---
title: "celcius"
author: "Arian Barakat, Rebin Hosini, Carles Sans"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{celcius}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

************************************************

##Introduction

The celcius package include functions for solving the knapsack problem through different of types of programming approaches. The included approaches/functions are: 

- brute_force_knapsack
- knapsack_dynamic
- greedy_knapsack

To use the functions, following packages are required: **parallel, stats and combinat**


************************************************

## Function usage

###data generation

```{r}
library(celcius)
knapsack_objects <- knapsack_data_gen(n = 2000, seed = 42)
head(knapsack_objects, n = 5)
```


### brute_force_knapsack

$brute_force_knapsack$ implements a function where you call knapsack brute force(x, W) that takes a data.frame cx with two variables v and w and returns the maximum knapsack value and which elements (rows in the data.frame). The variable W is the knapsack size:

```{r, warning= FALSE, message= FALSE}
brute_force_knapsack(knapsack_objects[1:8,], W = 3500)
```


### knapsack_dynamic
This function should return the same results as the brute force algorithm, but unlike the brute force it should scale much better since the algorithm will run in O(Wn)

```{r}
knapsack_dynamic(knapsack_objects[1:8,], W = 3500)
```

### greedy_knapsack
This algorithm will not give an exact result (but it can be shown that it will return at least 50% of the true maximum value), but it will reduce the computational complexity considerably to O(n log n) 

### Benchmarking

```{r, echo=TRUE, eval=FALSE}
library(microbenchmark)

knapsack_object_brute <- knapsack_data_gen(n = 16)
knapsack_object_dynamic <- knapsack_data_gen(n = 500)
knapsack_object_greedy <- knapsack_data_gen(n = 1000000)

microbenchmark(
  "Brute Normal" = brute_force_knapsack(x = knapsack_object_brute, W = 3500),
  "Brute Parallel" = brute_force_knapsack(x = knapsack_object_brute, W = 3500, parallel = TRUE),
  "Dynamic" = knapsack_dynamic(x = knapsack_object_dynamic, W = 3500),
  "Greedy" = greedy_knapsack(x = knapsack_object_greedy, W = 3500),
  times = 1
)
```


```{r, echo=TRUE, eval=FALSE}
Unit: seconds
           expr       min        lq      mean    median        uq       max neval
   Brute Normal  2.718805  2.718805  2.718805  2.718805  2.718805  2.718805     1
 Brute Parallel  1.693102  1.693102  1.693102  1.693102  1.693102  1.693102     1
        Dynamic 82.915175 82.915175 82.915175 82.915175 82.915175 82.915175     1
         Greedy  1.109075  1.109075  1.109075  1.109075  1.109075  1.109075     1

```


