---
title: "celcius"
author: "Arian Barakat, Rebin Hosini, Carles Sans"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{celcius}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

##Introduction

The celcius package implements methods for solving the knapsack problem with the application of several brute force functions: 

- brute_force_knapsack
- knapsack_dynamic
- greedy_knapsack

To use both functions, it is **required to have the packages parallel and combinat installed**

## Function usage

###data generation

```{r}
library(celcius)
knapsack_objects <- knapsack_data_gen(n = 2000, seed = 42)
head(knapsack_objects, n = 5)
```


### brute_force_knapsack

$brute_force_knapsack$ implements a function where you call knapsack brute force(x, W) that takes a data.frame cx with two variables v and w and returns the maximum knapsack value and which elements (rows in the data.frame). The variable W is the knapsack size:

```{r, warning= FALSE, message= FALSE}
brute_force_knapsack(knapsack_objects[1:8,], W = 3500)
```


### knapsack_dynamic
This function should return the same results as the brute force algorithm, but unlike the brute force it should scale much better since the algorithm will run in O(Wn)

```{r}
knapsack_dynamic(knapsack_objects[1:8,], W = 3500)
```

### greedy_knapsack
This algorithm will not give an exact result (but it can be shown that it will return at least 50% of the true maximum value), but it will reduce the computational complexity considerably to O(n log n) 

```{r}
greedy_knapsack(knapsack_objects[1:8,], W = 3500)
```




