---
title: "celcius"
author: "Arian Barakat, Rebin Hosini, Carles Sans"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{celcius}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

##Introduction

The celcius package implements methods for solving the knapsack problem with the application of several brute force functions: 

- brute_force_knapsack
- knapsack_dynamic
- greedy_knapsack

To use both functions, it is **required to have the packages parallel and combinat installed**

## Function usage

### brute_force_knapsack

brute_force_knapsack implements a function where you call knapsack brute force(x, W) that takes a data.frame cx with two variables v and w and returns the maximum knapsack value and which elements (rows in the data.frame). The variable W is the knapsack size:

```{r}
#library(celcius)
#brute_force_knapsack(knapsack_objects[1:8,], W = 3500)
```


### knapsack_dynamic

```{r}
#library(celcius)
#knapsack_dynamic(knapsack_objects[1:8,], W = 3500)
```

### greedy_knapsack

```{r}
#library(celcius)
#greedy_knapsack(knapsack_objects[1:8,], W = 3500)
```


## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
